---
title: "Distribution of mosquito species in Hermosillo, Sonora"
author: " Laboratorio de entomología médica, MScD Javier E. Verdugo M. "
date: "2025-06-17"
output: html_document
---
```{r setup, include=FALSE}
library(sf)
library(leaflet)
library(leaflet.extras)
library(leaflet.extras2)
library(lubridate)
library(dplyr)
library(htmlwidgets)
library(glue)
```

## Introduction

Mosquito surveillance is a key component in vector-borne disease control. Adult mosquito collection allows for early detection of vector species that may be involved in the transmission of viruses such as dengue, Zika, chikungunya, and West Nile virus. Identifying species abundance over time helps guide public health strategies and mitigate outbreaks effectively.

## Annual Species Abundance Maps

Below are links to yearly animated graphs showing the monthly abundance of mosquito species in Hermosillo from 2019 to 2025.

```{r results='asis', echo=FALSE}
# Vector de años
años <- 2019:2025

# Generar links en formato HTML
for (a in años) {
  cat(sprintf("- [%s](graficas/abundancia_mosquitos_%d.gif)\n", paste("GIF:", a), a))
}

```


## Interactive maps by year


Below are links to heat maps of mosquito abundance per block, for the generations generated per year:

```{r enlaces-mapas-anuales, echo=FALSE, results='asis'}

# Años que cubren tus datos
años <- 2019:2025

# Crear los enlaces dinámicamente
enlaces <- glue("- [Mapa de {años}](mapas_interactivos/mapa_calor_manzanas_{años}.html)")

# Mostrar los enlaces en formato Markdown
cat(enlaces, sep = "\n")


```

## Interactive maps by genere of mosquito

Below are links to heat maps of mosquito abundance by block, for mosquito genera:

```{r enlaces-mapas-especies, echo=FALSE, results='asis'}


# Géneros que cubren tus datos
Especies <- c("aedes", "anopheles")

# Crear enlaces normales
enlaces1 <- glue("- [Mapa de {Especies}](mapas_interactivos/mapa_calor_{Especies}.html)")

# Crear enlaces por año
enlaces2 <- glue("- [Mapa de {Especies} por año](mapas_interactivos/mapa_calor_{Especies}_por_año.html)")

# Mostrar ambos bloques de enlaces
cat(enlaces1, sep = "\n")

cat("\n\n")  # Salto de línea
cat(enlaces2, sep = "\n")

```
